Meta-analysis of the Interoceptive Accuracy Scale (IAS)

### 2025-01-15 analysis/Stud1_a.qmd
remove https

# APA style ####
gt_apastyle <- function(gt_table, font.size=12) {
  gt_table  |> 
    gt::opt_table_lines(extent = "none") %>%
    gt::tab_options(
      heading.border.bottom.width = 2,
      heading.border.bottom.color = "black",
      heading.border.bottom.style = "solid",
      table.border.top.color = "black",
      table.border.top.style = "solid",
      table.border.top.width = 2,  
      table_body.hlines.color = "white",
      table_body.border.top.color = "black",
      table_body.border.top.style = "solid",
      table_body.border.top.width = 2,
      heading.title.font.size = font.size,
      table.font.size = font.size,
      heading.subtitle.font.size = font.size,
      table_body.border.bottom.color = "black",
      table_body.border.bottom.width = 2,
      table_body.border.bottom.style = "solid",
      column_labels.border.bottom.color = "black",
      column_labels.border.bottom.style = "solid",
      column_labels.border.bottom.width = 1
    ) |> 
      gt::opt_table_font(font = "times")
}

@@

# Create the dataframe
table <- data.frame(
   Sample = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Makowski et al., (2023c)', 'Poreiro et al., (2024)', 'Poreiro et al., unpublished', 'Total'),
  Subsample = c('', 'Sample 1', 'Sample 2', '', '', '', '', '', '', 'Sample 1', 'Sample 2', 'Sample 3', '', 'Sample 1', 'Sample 2', '', '', '', '', '','', ''),   
  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', 'English', 'English', 'English',''),
  N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), nrow(df5_attention), nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10a), nrow(df10b), nrow(df10c), nrow(df11a), nrow(df11b), 32214),
  'Difference' = c('','', '', '', '', '', '', '', '', '', '', '', '', 'Collapsed "Itch" and "Tingling"', 'Collapsed "Itch" and "Tingling"', '', 'Analog scales', 'Analog scales', 'Analog scales', '', '', ''),
  Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "48.6.6 ± 14.1*", make_age(df5_attention$Age), make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10a$Age), make_age(df10b$Age), make_age(df10c$Age), make_age(df11a$Age), make_age(df11b$Age), '48.6 ± 13.1'),
  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76','18-50', '18-57', '18-60', '17-93'),
  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', '50%*', '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '76%', '74.8%', '75.9%', '71.6%'),
  Availability= c('', '', 'https://osf.io/3m5nh', 'https://osf.io/5x9sg', 'https://osf.io/j6ef3', 'https://osf.io/ms354', 'https://osf.io/mp3cy', 'https://osf.io/xwz6g', '', '', 'https://osf.io/3f2h6', '','','', 'https://osf.io/3eztd', 'https://osf.io/7p9u5', 'https://github.com/RealityBending/IllusionGameReliability', 'https://github.com/DominiqueMakowski/PHQ4R', 'https://github.com/RealityBending/InteroceptionPrimals', 'https://osf.io/49wbv', '','')
)

table_apa <- table |> 
  gt() |>
  cols_align(align = c("right"), columns = "Age") |> 
  cols_label(Age = "Age (Mean  ± SD)", Female_Percentage = "Female %") |> 
  tab_footnote("* Information taken from the sample description of relevant paper rather than recomputed.") |> 
  gt_apastyle()

table_apa
gtsave(table_apa, "figures/table1.tex")
gtsave(table_apa, "figures/table1.png")
```

>>>>

# APA style ####
gt_apastyle <- function(gt_table, font.size=12) {
  gt_table  |> 
    gt::opt_table_lines(extent = "none") %>%
    gt::tab_options(
      heading.border.bottom.width = 2,
      heading.border.bottom.color = "black",
      heading.border.bottom.style = "solid",
      table.border.top.color = "black",
      table.border.top.style = "solid",
      table.border.top.width = 2,  
      table_body.hlines.color = "white",
      table_body.border.top.color = "black",
      table_body.border.top.style = "solid",
      table_body.border.top.width = 2,
      heading.title.font.size = font.size,
      table.font.size = font.size,
      heading.subtitle.font.size = font.size,
      table_body.border.bottom.color = "black",
      table_body.border.bottom.width = 2,
      table_body.border.bottom.style = "solid",
      column_labels.border.bottom.color = "black",
      column_labels.border.bottom.style = "solid",
      column_labels.border.bottom.width = 1,
      latex.use_longtable = FALSE
    ) |> 
      gt::opt_table_font(font = "times")
}

@@

# Create the dataframe
table <- data.frame(
   Sample = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Makowski et al., (2023c)', 'Poreiro et al., (2024)', 'Poreiro et al., unpublished', 'Total'),
  Subsample = c('', 'Sample 1', 'Sample 2', '', '', '', '', '', '', 'Sample 1', 'Sample 2', 'Sample 3', '', 'Sample 1', 'Sample 2', '', '', '', '', '','', ''),   
  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', 'English', 'English', 'English',''),
  N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), nrow(df5_attention), nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10a), nrow(df10b), nrow(df10c), nrow(df11a), nrow(df11b), 32214),
  'Difference' = c('','', '', '', '', '', '', '', '', '', '', '', '', 'Collapsed "Itch" and "Tingling"', 'Collapsed "Itch" and "Tingling"', '', 'Analog scales', 'Analog scales', 'Analog scales', '', '', ''),
  Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "48.6.6 ± 14.1*", make_age(df5_attention$Age), make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10a$Age), make_age(df10b$Age), make_age(df10c$Age), make_age(df11a$Age), make_age(df11b$Age), '48.6 ± 13.1'),
  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76','18-50', '18-57', '18-60', '17-93'),
  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', '50%*', '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '76%', '74.8%', '75.9%', '71.6%'),
  Availability= c('', '', 'osf.io/3m5nh', 'osf.io/5x9sg', 'osf.io/j6ef3', 'osf.io/ms354', 'osf.io/mp3cy', 'osf.io/xwz6g', '', '', 'osf.io/3f2h6', '','','', 'osf.io/3eztd', 'osf.io/7p9u5', 'github.com/RealityBending/IllusionGameReliability', 'github.com/DominiqueMakowski/PHQ4R', 'github.com/RealityBending/InteroceptionPrimals', 'osf.io/49wbv', '','')
)

table_apa <- table |> 
  gt() |>
  cols_align(align = c("right"), columns = "Age") |> 
  cols_label(Age = "Age (Mean  ± SD)", Female_Percentage = "Female %") |> 
  tab_footnote("* Information taken from the sample description of relevant paper rather than recomputed.")

gt_apastyle(table_apa, font.size=12)
gtsave(gt_apastyle(table_apa, font.size=9), "figures/table1.tex")

# gtsave(table_apa, "figures/table1.png")
```
